Welcome to the \textbf{USAYNO}, a twelve-part question where each part has a yes/no answer. If you provide $C$ correct answers, your score on this problem will be $\frac{C}{6}$.

Your answer should be a twelve-character string containing `Y' (for yes) and `N' (for no). For instance if you think a, c, and f are `yes' and the rest are `no', you should answer YNYNNYNNNNNN.

\begin{itemize}

\item[(a)] Is there a positive integer $n$ such that the sum of the digits of $2018n+1337$ in base $10$ is $2018$ more than the sum of the digits of $2018n+1337$ in base $4$?

\item[(b)] Is there a fixed constant $\theta$ such that for all triangles $ABC$ with $$2018AB^2=2018CA^2+2017CA\cdot CB+2018CB^2,$$ one of the angles of $ABC$ is $\theta$?

\item[(c)] Adam lists out every possible way to arrange the letters of ``CCACCACCA'' (including the given arrangement) at $1$ arrangement every $5$ seconds. Madam lists out every possible way to arrange the letters of ``CCACCAA'' (including the given arrangement) at $1$ arrangement every $12$ seconds. Does Adam finish first?

\item[(d)] Do there exist real numbers $a,b,c$, none of which is the average of the other two, such that \[\frac{1}{b+c-2a}+\frac{1}{c+a-2b}+\frac{1}{a+b-2c}=0?\]

\item[(e)] Let $f\left(x\right)=\frac{2^x-2}{x}-1$. Is there an integer $n$ such that $$f\left(n\right),f\left(f\left(n\right)\right),f\left(f\left(f\left(n\right)\right)\right),\ldots$$ are all integers?

\item[(f)] In an elementary school with $2585$ students and $159$ classes (every student is in exactly one class), each student reports the size of their class. The principal of the school takes the average of all of these numbers and calls it $X$. The principal then computes the average size of each class and calls it $Y$. Is it necessarily true that $X>Y$?

\item[(g)] Six sticks of lengths $3$, $5$, $7$, $11$, $13$, and $17$ are put together to form a hexagon. From a point inside the hexagon, a circular water balloon begins to expand and will stop expanding once it hits any stick. Is it possible that once the balloon stops expanding, it is touching each of the six sticks?

\item[(h)] A coin is biased so that it flips heads and tails (and only heads or tails) each with a positive rational probability (not necessarily $\frac{1}{2}$). Is it possible that on average, it takes exactly twice as long to flip two heads in a row as it is to flip two tails in a row?

\item[(i)] Does there exist a base $b$ such that $2018_b$ is prime?

\item[(j)] Does there exist a sequence of $2018$ distinct real numbers such that no $45$ terms (not necessarily consecutive) can be examined, in order, and be in strictly increasing or strictly decreasing order?

\item[(k)] Does there exist a scalene triangle $ABC$ such that there exist two distinct rectangles $PQRS$ inscribed in $\triangle{ABC}$ with $P\in AB$, $Q,R\in BC$, $S\in AC$ such that the angle bisectors of $\angle{PAS}$, $\angle{PQR}$, and $\angle{SRQ}$ concur?

\item[(l)] For three vectors $\mathbf{u}_1,\mathbf{u}_2,\mathbf{u}_3$ with $\mathbf{u}_i=\left(x_{i,1},x_{i,2},x_{i,3},x_{i,4}\right)$, define \[f\left(\mathbf{u}_1,\mathbf{u}_2,\mathbf{u}_3\right)=1-\displaystyle\prod_{j=1}^4\left(1+\left(x_{2,j}-x_{3,j}\right)^2+\left(x_{3,j}-x_{1,j}\right)^2+\left(x_{1,j}-x_{2,j}\right)^2\right).\] Are there any sequences $\mathbf{v}_1,\mathbf{v}_2,\ldots,\mathbf{v}_{18}$ of distinct vectors with four components, with all components in $\left\{1,2,3\right\}$, such that \[\displaystyle\prod_{1\leq i<j<k\leq18}f\left(\mathbf{v}_i,\mathbf{v}_j,\mathbf{v}_k\right)\equiv1\pmod3?\]