Given a permutation $\pi$, let $f$ be a function such that $f\left(i\right)$ is the number of $j<i$ such that $\pi\left(j\right)>\pi\left(i\right)$, so $f\left(i\right)$ is an integer between $0$ and $i-1$, inclusive. I claim that the process of creating $f$ from $\pi$ is reversible. That is, there is a bijection between $f$ satisfying $f\left(i\right)\in\left[0,i-1\right]$ and permutations $\pi$. Start with a list with $1$ in it. Suppose that the list contains $1,2,\ldots,k-1$. Then there are $k$ possible spaces to put $k$ in the list (front, back, or any of the gaps between the current elements of the list). Put $k$ at the space $f\left(k\right)+1$ from the right. So if $f\left(k\right)=0$, put $k$ at the back of the list; if $f\left(k\right)=1$, put $k$ right before the last element of the list. Then the definition of $f$ is satisfied, so we can construct $\pi$ this way. So we have a bijection between the $\pi$ and the $f$.
	
	Now, fix $f\left(i\right)$ for $i\neq5$ and note that the number of inversions of $\pi$ is $S=\displaystyle\sum_{i=1}^8f\left(i\right)$. We can vary $f\left(5\right)$ between $0$ and $4$ to hit every residue mod $5$ for $S$, so there is a unique value of $f\left(5\right)$ which gives that $S\equiv0\pmod5$. Thus, we just want to count the number of ways we can fix the $f\left(i\right)$ and this is $\frac{8!}{5}=\boxed{8064}$.
	
	Alternate solution: Let $G_n\left(x\right)=\displaystyle\sum_{i=0}^{\binom{n}{2}}a_{n,i}x^i$, where $a_{n,i}$ is the number of permutations of $\left\{1,2,\ldots,n\right\}$ that have exactly $i$ inversions. I claim that \[G_n\left(x\right)=\frac{x^n-1}{x-1}G_{n-1}\left(x\right)\] for $n\geq2$. Suppose that $n$ is in $a$ inversions. Then the generating function for the number of permutations with exactly $i$ inversions is $x^aG_{n-1}\left(x\right)$ because the rest of the inversions are equivalent to inversions on permutations of $\left\{1,2,\ldots,n-1\right\}$. So $G_n$ is just the sum of this over $a=0,1,\ldots,n-1$, which is the desired equality. Then since $G_1\left(x\right)=1$, we can induct and see that \[G_n\left(x\right)=\frac{x-1}{x-1}\cdot\frac{x^2-1}{x-1}\cdots\frac{x^n-1}{x-1}.\] Now, let $b$ be a positive integer at most $n$ and $a$ a non-negative integer less than $b$. I claim that the number of permutations of $\left\{1,2,\ldots,n\right\}$ that have $a\pmod b$ inversions is $\frac{n!}{b}$. That is, the number of inversions is equidistributed $\pmod b$ for any $b\leq n$. By Roots of Unity filter, this count is $\frac{1}{b}\displaystyle\sum_{r}\frac{G_n\left(r\right)}{r^a}$, where the sum is over all roots $r$ of $x^b-1$. But clearly $G_n\left(1\right)=n!$ and $G_n\left(r\right)=0$ for $r\neq1$, so this count is $\frac{n!}{b}$ and this is true. In the problem with $n=8$ and $b=5$, the count is $\boxed{8064}$.