By 2010 USAJMO \#5, $m=1006$ works. I claim that this is the answer. It suffices to prove that $m=1005$ fails.

Let $P$ be the set of $1005$ permutations that we choose. Consider a bipartite graph on two copies of vertices labelled $1,2,\ldots,2010$. Connect $i$ on the left with $j$ on the right iff $\pi\left(i\right)\neq j$ for each $\pi\in P$. To show that $m=1005$ fails, we need to show that we can choose some permutation $\sigma$ such that $i$ on the left and $\sigma\left(i\right)$ on the right are connected. Equivalently, we wish to show that there exists a perfect matching.

Consider a non-empty subset $S$ of $\left\{1,2,\ldots,2010\right\}$. Let $N\left(S\right)$ be the neighbor set of $S$ when treating the elements of $S$ as vertices on the left. I claim that $\left|N\left(S\right)\right|\geq\left|S\right|$. Observe that for any $i$ on the left, there are at least $1005$ elements $j$ on the right that are connected with $i$. This is because there are at most $1005$ values of $\pi\left(i\right)$, so at least $1005$ of the vertices on the right satisfy the condition to be connected. Thus, $\left|N\left(S\right)\right|\geq1005$. If $\left|S\right|\leq1005$, the claim is true. Otherwise, $\left|S\right|\geq1006$. Take a vertex $j$ on the right. Observe that $\left\{\pi^{-1}\left(j\right)\mid\pi\in P\right\}$ has at most $1005$ elements, so there is some element $i$ in $S$ which is not in this set. Then $i$ on the left and $j$ on the right are connected, so $j\in N\left(S\right)$. Then $\left|N\left(S\right)\right|=2010$ and thus the claim is true.

Then by Hall's Marriage Theorem, there is a perfect matching in the graph and hence $1005$ fails.